### 2021-04-21 input/conclusion.tex
on implem and complexity wip
backport end of the introduction into the conclusion

@@

>>>>

%% \noindent We propose an implementation that further decreases
%% generated traffic and improves on
%% anonymity~\cite{whitaker2002forwarding}.  \NAME makes extensive use of
%% paths to enable deleting messages without incrementing local
%% counters. Messages carry their respective path and processes detect
%% when such messages have been looping when they carry their identity
%% (see Lines~\ref{line:notloopingA} and \ref{line:notloopingB} of
%% Algorithm~\ref{algo:adddelundo}). Since membership is all that
%% matters, we propose to trade vectors of identities for Bloom
%% filters~\cite{almeida2007scalable}. Processes know with high
%% probability if they already received and forwarded each message
%% without knowing the identity of all processes that received it.  False
%% positive probability only incurs premature stopping of broadcast
%% messages and does not invalidate the delete of specific
%% messages. \TODO{Rework.}

@@

% TODO : Use cases
While we use the distance to the closest copy in this paper, It is
notewothy that other scopes can be envisioned according to the
use-cases.  For instance, the location of a city in order to broadcast
message to all nodes in the city.  This requires nodes to store and
maintain their city location in their local state. Nodes stop
delivering and forwarding their received messages when they come from
a different city. Such a predicate can be complexified in order to
broadcast messages to all nodes in the city plus neighboring
cities. This requires nodes to overload forwarded messages the first
time they reach another city. The predicate checks if messages already
reached two distinct cities before delivery.  The predicate can even
be piggypack within the message and so be different for each
message.\TODO{Complete the use-cases}
